---
title: "Performance Challenge"
author: "Florian Privé"
date: "June 16, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem

I have this function to generate `K` times an ordered vector of `n2` elements sampled from `n` elements (without replacement).

```{r}
gen <- function(K, n, n2) {
  withr::with_seed(1, replicate(K, sort(sample(n, n2))))
}
gen(K = 6, n = 5, n2 = 2)
```

I want to transform this integer matrix in a list of integer vectors specifying for a given value (from 1 to `n`) which columns contain this specific value:

```{r}
naive_solu <- function(mat, n) {
  
  res <- list()
  for (i in seq_len(n)) {
    res[[i]] <- which(mat == i, arr.ind = TRUE)[, 2]
  }
  res
}
naive_solu(gen(K = 6, n = 5, n2 = 2), n = 5)
```

## Performance

The problem with this naive solution is that if I want to apply it for larger values, it would be slow:

```{r}
K <- 100; n <- 10e3; n2 <- 2e3
mat <- gen(K, n, n2)
system.time(naive_solu(mat, n))
```

Can you provide a faster solution? Using {Rcpp} is allowed here. Please send me your solution at florian.prive.21 \<at\> gmail.com. 

I'll compile and comment the results in a blog post on June 20.
